POMDP comparisons across sigma_m, sigma_g

### 2018-01-30 appendix/appendixA.Rmd
no author (double-blind)

---
title: "Appendix A: Code and supplementary figures for simulation and policy analyis"
author: "Carl Boettiger"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
bibliography: ../manuscripts/citations.bib

>>>>

---
title: "Appendix A: Code and supplementary figures for simulation and policy analyis"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
bibliography: ../manuscripts/citations.bib

### 2018-01-30 appendix/appendix_recruit_first.Rmd
no author (double-blind)

---
title: "POMDP comparisons across sigma_m, sigma_g"
author: "Carl Boettiger"
date: "`r Sys.Date()`"
output: 
  github_document: default
  pdf_document: default
---

@@

write_csv(sims, "appendix_files/sims.csv")
```

@@

write_csv(policy_table, "appendix_files/policy_table.csv")
```

>>>>

---
title: "POMDP comparisons across sigma_m, sigma_g"
date: "`r Sys.Date()`"
output: 
  github_document: default
  pdf_document: default
---

@@

write_csv(sims, file.path(log_dir, "sims.csv"))
```

@@

write_csv(policy_table, file.path(log_dir, "policy_table.csv"))
```
